

\subsection{Connection with the Explorer tool from the C++-API}
\label{sec:conn_from_cpp_api}

TBC

\subsection{Connection with the Explorer tool from the XML-API}
\label{sec:conn_from_cpp_api}

TBC

\subsection{Fatality of Errors for Exploration}
\label{sec:error_fatality_for_exploration}

The user can configure the fatality of an error during the simulation.
Such fatality is an attribute exported to the output XML file whenever 
an error condition has been reported.

By default, KisTA states that a simulation error will produce a \texttt{non-fatal} error.
%
This enables the exploration tool to discard the results of the current configuration, 
and continue the exploration looking for other configurations.

However, the user might want to immediately stop the exploration in case
an error is reported. 
%
A use case is one where a functional validation of each
implementation alternatives explored (explained in Section~\ref{sec:functional_validation})
is performed at the same time the exploration is performed.
%

\subsubsection{C++ API}
\label{sec:error_fatality_for_exploration}

For controling the fatality for the the exploration of an error,
KisTA provides the API shown in Listing~\ref{list:fatality_error_4explor}.

%\begin{table}[t]
\begin{lstlisting}[style=KistaCodeStyle,caption={API for controling the fatality for the exploration of an error.},label=list:fatality_error_4explor]
void set_error_stop_exploration();
void set_error_does_not_stop_exploration(); // set by default
bool &error_stop_exploration();
\end{lstlisting}
%\end{table}

An error can be settled as fatal for the exploration through the \texttt{set\_error\_stop\_exploration} function.
This function can be called at any time (even after simulation start).
%
Therefore, the \texttt{set\_error\_does\_not\_stop\_exploration} function enables a full control of the simulation gaps
where an error should be considered fatal or not.

The \texttt{error\_stop\_exploration} function enables to read the current state of the fatality flag.

\subsubsection{XML API}
\label{sec:error_fatality_for_exploration}

The KisTA XML API enables also setting the fatality of an error for the exploration.
%
However, it must be considered that it will be settled only at elaboration time, before the simulation start.
%

Listing~\ref{list:fatality_error_4explor} reports how it can be settled with the \texttt{error\_fatality\_for\_exploration} option
within the configuration settings section.

%\begin{table}[t]
\begin{lstlisting}[language=XML, caption={Setting the fatality for the exploration from the XML interface.}, label=list:xml_fatality_setting]
<kista_configuration>
        ...
    <error_fatality_for_exploration value="true">
        ...
</kista_configuration>
\end{lstlisting}
%\end{table}

